---
title: "R Notebook"
output: 
  html_document: 
    keep_md: yes
    self_contained: no
    dev: 'svg'
    code_folding: hide
---

```{r results='hide', warning=F, message=F}
library(tidyverse)
library(magrittr)
library(lme4)
library(broom)
library(eoinR)
# source('../HelperFunctions.R')
select = dplyr::select
theme_set(cowplot::theme_cowplot(font_size = 20))
data = read.csv('data/all_trial_metadata.csv')
z = function(x){ scale(x, center=T, scale=T) %>% c}

data = mutate(data,
              participant = factor(participant),
              outcome = 1 - is.na(outcome),
              bet = ifelse(condition==0, action, 1-action),
              prob = p_win,
              win = v_win,
              c.prob = prob - .5,
              c.win = win - 10,
              z.prob = z(prob),
              z.win = z(win),
              ev = win * prob - 10*(1-prob),
              f.condition = factor(condition),
              f.bet = factor(bet),
              act = rt > -1,
              rt = ifelse(act, rt, NA),
              change = 1*(bet!=lag(bet, 1)),
              change.phase = c(0, cumsum(change[2:length(change)])),
              action.type=interaction(visible, difficult) %>% fct_recode(Guess='0.False', Choose='1.False', Pick='1.True') %>% droplevels(),
              action.type = fct_relevel(action.type, "Choose", "Pick", "Guess"),
              action.type.r = fct_relevel(action.type, "Guess", "Pick", "Choose"))
levels(data$participant) = 1:length(levels(data$participant))
levels(data$f.condition) = list('Act-to-bet'=0, 'Act-to-pass'=1)
levels(data$f.bet) = list('Bet'=1, 'Pass'=0)
data %<>% data.frame()
lgnd = function(x,y) theme(legend.position = c(x,y), legend.justification = c(x, y))

choices = filter(data, visible==1)
guesses = filter(data, visible==0)

colours = c('darkgreen', 'red', 'black')
order = c('Choose', 'Pick', 'Guess')

str(data)
```



# Actual responses

```{r fig.width=6.25, fig.height=5} 
choices %>%
  group_by(win, prob) %>%
  summarise(bet=mean(bet)) %>%
  ggplot(aes(win, prob, fill=bet)) +
  geom_tile() +
  scale_fill_gradient2(low='blue', mid='yellow', high='red', midpoint=.5) +
  geom_text(aes(label=round(bet, 2))) +
  labs(x='Value(Win)', y='P(Win)', fill='P(Bet)') +
  scale_x_continuous(breaks = seq(2, 18, 2)) +
  scale_y_continuous(breaks = seq(.2, .8, .1)) +
  theme_bw(base_size = 20)
```

```{r fig.width=10, fig.height=5} 
choices %>%
  group_by(f.condition, win, prob) %>%
  summarise(bet=mean(bet)) %>%
  ggplot(aes(win, prob, fill=bet)) +
  facet_wrap(~f.condition) +
  geom_tile() +
  scale_fill_gradient2(low='blue', mid='yellow', high='red', midpoint=.5) +
  geom_text(aes(label=round(bet, 2))) +
  labs(x='Value(Win)', y='P(Win)', fill='P(Bet)') +
  scale_x_continuous(breaks = seq(2, 18, 2)) +
  scale_y_continuous(breaks = seq(.2, .8, .1)) +
  theme_bw(base_size = 20)
```

```{r fig.width=7, fig.height=5} 
choices %>%
  group_by(participant, win, prob) %>%
  summarise(bet=mean(bet)) %>%
  ggplot(aes(win, prob, fill=bet)) +
  facet_wrap(~participant, nrow=5) +
  geom_tile() +
  scale_fill_gradient2(low='blue', mid='yellow', high='red', midpoint=.5) +
  # geom_text(aes(label=round(bet, 2))) +
  labs(x='Value(Win)', y='P(Win)', fill='P(Bet)') +
  scale_x_continuous(breaks = seq(2, 18, 8)) +
  scale_y_continuous(breaks = seq(.2, .8, .3)) +
  theme_bw(base_size = 20) +
  theme(strip.background = element_blank(), strip.text.x = element_blank())
```


The interaction model fits best overall.
I think that this is only driven by a subset of participants though.
Unfortunately, I can't fit random effects for the interaction, although this does support my belief.

```{r}
resp.model.0 = glmer(bet ~ 1 + (1|participant), data=choices, family = binomial)
resp.model.ev = glmer(bet ~ ev + (ev|participant),  data=choices, family = binomial)
resp.model.value = glmer(bet ~ c.win + (c.win|participant), data=choices, family = binomial)
resp.model.prob =  glmer(bet ~ c.prob + (c.prob|participant), data=choices, family = binomial)

resp.model.both = glmer(bet ~ c.win + c.prob + (c.win + c.prob|participant), 
                            data=choices, family = binomial)
resp.model.interaction = glmer(bet ~ c.win * c.prob + (c.win + c.prob|participant), 
                               data=choices, family = binomial)
# response.models = list(m0=resp.model.0, m.ev=resp.model.ev, m.val=resp.model.value, 
#                        m.prob=resp.model.prob, m.both=resp.model.additive, mX=resp.model.interaction) 
# nmns = names(response.models)
# names(response.models) = NULL
# a = do.call(anova, c(response.models))
# rownames(a) = nmns
# a
anova(resp.model.0, resp.model.ev, resp.model.value, resp.model.prob, resp.model.both, resp.model.interaction) %>% data.frame
```

### Visualise individual models

```{r fig.width=16, fig.height=3}
plot.data = data %>%
  group_by(c.prob, c.win, ev) %>% 
  summarise(n=n())

response.models = list(m0=resp.model.0, m.ev=resp.model.ev, m.val=resp.model.value, 
                       m.prob=resp.model.prob, m.both=resp.model.both, mX=resp.model.interaction) 
for(m in names(response.models)) {
  plot.data[m] = predict(response.models[[m]], newdata=plot.data, re.form=NA, type='response')
}
d = plot.data %>% gather(model, y, m0:mX)
d$model = d$model %>% factor() %>% 
  fct_recode(Intercept='m0', EV='m.ev', Amount='m.val', 
             Probability='m.prob', Both='m.both', Interaction='mX') %>%
  fct_relevel('Intercept', 'Amount', 'Probability', 'EV', 'Both', 'Interaction')

ggplot(d, aes(c.win, c.prob, fill=y)) +
  facet_wrap(~model, ncol = 6) +
  geom_tile() +
  scale_fill_gradient2(low='blue', mid='yellow', high='red', midpoint=.5) +
  labs(x='Value(Win)', y='P(Win)', fill='P(Bet)') +
  scale_x_continuous(breaks = seq(2, 18, 8)) +
  scale_y_continuous(breaks = seq(.2, .8, .3)) +
  theme_bw(base_size = 20)
```


## Subject-specific models

```{r fig.width=30, fig.height=2.5} 
subj.plot.data = choices %>%
  group_by(participant, win, prob, c.win, c.prob) %>%
  summarise(bet=mean(bet))

ggplot(subj.plot.data, aes(win, prob, fill=bet)) +
  facet_wrap(~participant, ncol=20) +
  geom_tile() +
  scale_fill_gradient2(low='blue', mid='yellow', high='red', midpoint=.5) +
  # geom_text(aes(label=round(bet, 2))) +
  labs(x='Value(Win)', y='P(Win)', fill='P(Bet)') +
  scale_x_continuous(breaks = seq(2, 18, 8)) +
  scale_y_continuous(breaks = seq(.2, .8, .3)) +
  theme_bw(base_size = 20) +
  theme(strip.background = element_blank(), strip.text.x = element_blank())
```

```{r}
subject.model.comparison = choices %>%
  nest(-participant) %>%
  mutate(m = map(data, function(d){
# Fit all possible models
    m.0          = glm(bet ~ 1                             , data = d, family=binomial)
    m.ev         = glm(bet ~ ev                            , data = d, family=binomial)
    m.win        = glm(bet ~ c.win                         , data = d, family=binomial)
    m.prob       = glm(bet ~ c.prob                        , data = d, family=binomial)
    m.win.prob   = glm(bet ~ c.win + c.prob                , data = d, family=binomial)
    m.win.probX  = glm(bet ~ c.win + c.prob + c.win:c.prob , data = d, family=binomial)
    comp = eoinR::compare.models(m.0, m.win, m.prob, m.ev, 
                                 m.win.prob, m.win.probX)# %>% select(model, AIC.prob, BIC.prob)
    return(comp)
  })) %>%
  unnest(m)
subject.model.comparison$participant %<>% factor()
levels(subject.model.comparison$participant) = 1:length(subject.model.comparison$participant)
subject.model.comparison$model %<>% factor
# levels(subject.model.comparison$model) = c('NullModel'='m.0', 'P(Win)'='m.prob', 'V(Win)'='m.win', 'EV'='m.ev',
#                                            '2xMain effects'='m.win.prob', '+Interaction'='m.win.probX')
```

```{r fig.width=12, fig.height=4}
d = subject.model.comparison
d$model = d$model %>% factor() %>% 
  fct_recode(Intercept='m.0', EV='m.ev', Amount='m.win', 
             Probability='m.prob', `A+P`='m.win.prob', `A×P`='m.win.probX') %>%
  fct_relevel('Intercept', 'Amount', 'Probability', 'EV', 'A+P', 'A×P')

d = filter(d, model %in% c('Probability', 'EV', 'A+P', 'A×P')) %>%
  mutate(model = droplevels(model))
ggplot(d, aes(participant, BIC.prob, fill=model)) +
  scale_x_discrete(breaks=c(5, 10, 15, 20)) +
   geom_bar(position = 'fill', stat='identity') +
  # facet_wrap(~f.condition) +
  labs(x='Subject', y='P(Model | data)', fill='Model')
```

```{r fig.width=6, fig.height=6}
ggplot(d, aes(participant, BIC.prob, fill=model)) +
  scale_x_discrete(breaks=c(5, 10, 15, 20)) +
   geom_bar(position = 'fill', stat='identity') +
  # facet_wrap(~f.condition) +
  labs(x='Subject', y='P(Model | data)', fill='Model') +
  coord_flip()
```


```{r}
# library(ggtern)
# subject.model.comparison %>%
#   select(participant, model, BIC.prob) %>%
#   spread(model, BIC.prob) %>%
#   ggtern(aes(x=m.win.prob, y=m.win.probX, z=m.ev)) +
#   geom_point() +
#   scale_L_continuous(limits=c(-.1, 1.2)) +
#   scale_R_continuous(limits=c(-.1, 1.2)) +
#   scale_T_continuous(limits=c(-.1, 1.2))
# 
# ggtern(subject.model.comparison,
#                     aes(x=x,y=y,z=z)) +
#   geom_polygon(alpha=0.5,color="red",size=2) +
#   geom_path(color="blue",linetype=2,size=1) +
#   geom_point(size=3,fill="yellow",color="red",shape=21) +
#   geom_smooth(method="lm",se=F,limitarea=F,fullrange=T,
#               color="magenta",size=1,linetype=3)
```


```{r}


mm = subject.model.comparison %>% 
  mutate(lmp = -.5*BIC) %>%
  select(model, participant, lmp) %>%
  spread(participant, lmp)

mm %>% gather(x, y, -model) %>% ggplot(aes(as.numeric(x), y, color=model, group=model)) + geom_point() + geom_path()

m = mm %>%
  select(-model) %>%
  as.matrix() %>%
  t() # subjects x models
## https://github.com/mattelisi/bmsR
bayes.model.comp = bmsR::VB_bms(m)
o = data.frame(model=as.character(mm$model), bayes.model.comp) %>%
  mutate_if(is.numeric, round, digits=2)
o
```


```{r}
subject.model.predictions = choices %>%
  nest(-participant) %>%
  mutate(predictions = map(data, function(d){
# Fit all possible models
    d$m0     = glm(bet ~ 1                             , data = d, family=binomial) %>% predict(type='response')
    d$m.ev   = glm(bet ~ ev                            , data = d, family=binomial) %>% predict(type='response')
    d$m.val  = glm(bet ~ c.win                         , data = d, family=binomial) %>% predict(type='response')
    d$m.prob = glm(bet ~ c.prob                        , data = d, family=binomial) %>% predict(type='response')
    d$m.both = glm(bet ~ c.win + c.prob                , data = d, family=binomial) %>% predict(type='response')
    d$mX     = glm(bet ~ c.win + c.prob + c.win:c.prob , data = d, family=binomial) %>% predict(type='response')
    return(d)
  }))

d = subject.model.predictions %>% unnest(predictions) %>%
  gather(model, pred.y, m0:mX)
d$model = d$model %>% factor() %>% 
  fct_recode(Intercept='m0', EV='m.ev', Amount='m.val', 
             Probability='m.prob', Both='m.both', Interaction='mX') %>%
  fct_relevel('Intercept', 'EV', 'Amount', 'Probability', 'Both', 'Interaction')

```

```{r fig.width=34, fig.height=12} 
d.mean = d %>% group_by(model, participant, win, prob) %>% summarise(pred.y=mean(pred.y)) 
d.plot.full = rbind(d.mean, 
      subj.plot.data %>% select(participant, win, prob, pred.y=bet) %>% mutate(model='DATA'))
d.plot.full$model %<>%
  fct_relevel('Intercept', 'Amount', 'Probability', 'EV', 'Both', 'Interaction', 'DATA')

ggplot(d.plot.full, aes(win, prob, fill=pred.y)) +
  facet_grid(model~participant) +
  geom_tile() +
  scale_fill_gradient2(low='blue', mid='yellow', high='red', midpoint=.5) +
  labs(x='Value(Win)', y='P(Win)', fill='P(Bet)') +
  scale_x_continuous(breaks = seq(2, 18, 8)) +
  scale_y_continuous(breaks = seq(.2, .8, .3)) +
  theme_bw(base_size = 20)
```


Model mimicry?

```{r}
m = lm(ev ~ c.win * c.prob, data=choices)
coef(m) %>% round(digits=2)
plot(predict(m), resid(m))
```

```{r}
m = lm(ev ~ win * prob, data=choices)
coef(m) %>% round(digits=2)
plot(predict(m), resid(m))
```

```{r}
subject.full.models = choices %>%
  nest(-participant) %>%
  mutate(coefs = map(data, function(d){
    m = glm(bet ~ c.win + c.prob + c.win:c.prob , data = d, family=binomial)
    tidy(m)
  })) %>% unnest(coefs)
refs = data.frame(term=c('(Intercept)', 'c.prob', 'c.win', 'c.win:c.prob'), ref=c(0, 20, .5, 1))
refs0 = data.frame(term=c('(Intercept)', 'c.prob', 'c.win', 'c.win:c.prob'), ref=c(NA, NA, NA, 0))

subject.full.models %>%
  group_by(term) %>%
  summarise(m=mean(estimate), sd=sd(estimate), sem=sd(estimate)/sqrt(n())) %>%
  inner_join(refs) %>%
  mutate(t = (m-ref)/sem)
```

```{r}

d = subject.full.models %>%
  select(participant, term, estimate) %>%
  spread(term, estimate) %>%
  mutate(sum = c.prob + c.win + `c.win:c.prob`, 
         adj = 21.5/sum,
         c.prob = c.prob*adj,
         c.win = c.win*adj,
         `c.win:c.prob` = `c.win:c.prob`*adj) %>%
  gather(term, estimate, `(Intercept)`, c.prob, c.win, `c.win:c.prob`)
d$term %<>% factor() %>% fct_recode(Intercept='(Intercept)', `P(Win)`='c.prob', `V(Win)`='c.win', Interaction='c.win:c.prob')
refs$term %<>% factor() %>% fct_recode(Intercept='(Intercept)', `P(Win)`='c.prob', `V(Win)`='c.win', Interaction='c.win:c.prob')
refs0$term %<>% factor() %>% fct_recode(Intercept='(Intercept)', `P(Win)`='c.prob', `V(Win)`='c.win', Interaction='c.win:c.prob')

ggplot(d, aes(as.numeric(participant), estimate)) +
  facet_wrap(~term, scales='free') +
  geom_point() +
  geom_hline(data=refs, mapping=aes(yintercept=ref), color='red', linetype='dashed') +
  geom_hline(data=refs0, mapping=aes(yintercept=ref), color='blue', linetype='dotted') +
  scale_x_continuous(breaks=c(10, 20)) +
  labs(x='Participant', y='Regression weight')

```

```{r}
d %>%
  group_by(term) %>%
  summarise(m=mean(estimate), sd=sd(estimate), n=n(), sem=sd(estimate)/sqrt(n())) %>%
  inner_join(refs) %>%
  mutate(t = (m-ref)/sem,
         p = pt(-abs(t), df=n-1)*2) %>%
  round_df(3)
```




```{r}
ggplot(subject.full.models, aes(participant, estimate)) +
  facet_wrap(~term, scales='free') +
  geom_point()
```

```{r}
ggplot(subject.full.models, aes(term, estimate)) +
  geom_point() +
  stat_summary(color='red', position=position_nudge(x=.2))
```
## Intercept by condition

```{r}
contrasts(choices$f.condition) = c(-.5, .5)
m.condition = glmer(bet ~ f.condition + c.win * c.prob + (c.win + c.prob|participant), 
                    data=choices, family = binomial)
summary(m.condition)
```

```{r fig.width=8, fig.height=3}
df = multcomp::glht(m.condition, 
                    linfct=rbind('Act-to-bet'=c(1, -.5, 0,0,0),
                                 'Act-to-pass'=c(1, +.5, 0,0,0))) %>% summary() %>% tidy() %>%
  mutate(lwr = estimate + std.error,
         upr = estimate - std.error)

df %>%
  mutate_if(is.numeric, invlogit) %>%
  ggplot(aes(lhs, estimate, ymin=lwr, ymax=upr)) +
  geom_point() +
  geom_linerange() +
  geom_hline(yintercept=.5, linetype='dashed') +
  labs(x='Condtion', y='P(Bet) ± SEM', title='P(Bet) estimated at mean of other predictors') +
  coord_flip(ylim=c(.2, .8))
```


```{r}
# m.conditin.guess = glmer(bet ~ )
```




# Bayesian Full Model

```{r}
library(brms)
library(glue)
default.prior = get_prior(bet ~ c.win * c.prob + (c.win * c.prob|participant),  data=choices, family = binomial)
my.prior = set_prior('normal(0, 50)', class='b')

refit = F
if(refit){
  brms.model = brm(bet ~ c.win * c.prob + (c.win * c.prob|participant),  data=choices, family = bernoulli,
                   prior=my.prior, chains=2, cores=2, iter=1000)
  saveRDS(brms.model, 'brms.model.rds')
} else {
  brms.model = readRDS('brms.model.rds')
}

samps = posterior_samples(brms.model)

brms.model


```



Normalise fixed effects

```{r fig.width=12, fig.height=3}
b = samps %>% select(starts_with('b_c.'))
names(b) %<>% str_remove_all('b_') %>% str_remove_all('c\\.')

refs = data.frame(term=c('prob', 'win', 'win:prob'), ref=c(20, .5, 1))
labeller = as_labeller(c('prob'='P(Win)', 'win'='V(Win)', 'win:prob'='P(Win) × V(Win)'))

b.adj = b / (apply(b, 1, sum)/21.5)

b.adj %>%
  gather(term, val) %>%
  group_by(term) %>%
  summarise_at(vars(val), funs(mean, q2.5, q97.5))


b.adj %>%
  gather(term, val) %>%
  ggplot(aes(val)) +
  facet_wrap(~term, scales='free', labeller = labeller) +
  geom_histogram(fill='skyblue', color='white', bins=30) +
  geom_vline(data=refs, mapping=aes(xintercept=ref), linetype='dashed') +
  scale_y_continuous(breaks=c()) +
  labs(x='Posterior density', y='')
```



```{r}
adj.ranfx = map(1:20, function(p){
  r = samps %>% select(starts_with(glue('r_participant[{p},c.')))
  co = r + b
  co.adj = co / (apply(co, 1, sum)/21.5)
  co.adj
})
adj.ranfx = do.call(cbind, adj.ranfx)

adj.ranfx.long = adj.ranfx %>%
  mutate(iter = 1:n()) %>%
  gather(term, val, -iter)  %>%
  mutate(subject = str_extract(term, '[0-9]+') %>% as.numeric(),
         coef    = str_extract(term, 'c\\..+?]') %>% str_remove_all('(c\\.)|\\]'))

point.subj.fx = adj.ranfx.long %>%
  group_by(subject, coef) %>%
  summarise(mean=mean(val))

```

```{r  fig.width=12, fig.height=4}
ord = point.subj.fx %>%
  filter(coef=='prob') %>%
  arrange(mean) %>%
  select(subject) %>%
  ungroup() %>%
  mutate(i = 1:n())

d = adj.ranfx.long %>%
  inner_join(ord, by=c('subject')) %>%
  mutate(subject = factor(subject) %>% fct_reorder(i))


ggplot(d, aes(i, val)) +
  stat_summary(fun.data=mean_95) +
  facet_wrap(~coef, scales='free', labeller = labeller) +
  geom_hline(data=mutate(refs, coef=term), mapping=aes(yintercept=ref), linetype='dashed') +
  coord_flip() +
  scale_x_continuous(breaks=NULL) +
  geom_blank(data=d) +
  labs(x=NULL, y='Regression weight')

```


# Combine plots



```{r fig.width=12, fig.height=4}
b.adj %>%
  gather(coef, val) %>%
  ggplot(aes(val)) +
  facet_wrap(~coef, scales='free', labeller = labeller) +
  geom_histogram(fill='skyblue', color='white', bins=30) +
  geom_vline(data=mutate(refs, coef=term), mapping=aes(xintercept=ref), linetype='dashed') +
  scale_y_continuous(breaks=c()) +
  geom_blank(data=d, mapping=aes()) +
  labs(x='Posterior density', y='')
```

```{r}

point.subj.fx %>%
  spread(coef, mean) %>%
  ggplot(aes(prob, win)) +
  geom_point()

point.subj.fx %>%
  spread(coef, mean) %>%
  with(., cor.test(prob, win))
```

